Indirect climate effects on biomass partitioning

### 2014-11-20 manuscript/draftpaper.Rnw
Changed order of figures, minor changes to (new) Fig 4 and (new) Fig 1
Fixed Figure SI2 (colors, removed glasshouse studies)

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{FigureSI-1_MAPMAT_vegetation.pdf}
    \caption{Mean annual precipitation and temperature for all contributed datasets, by vegetation type. Note that in this study, we did not include glasshouse studies.}
    \label{fig:figureSI1}
\end{figure}

>>>>

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{FigureSI-1_MAPMAT_vegetation.pdf}
    \caption{Mean annual precipitation (MAP) and temperature (MAT) for all contributed datasets, by vegetation type. MAP and MAT were taken from Worldclim \cite{worldclim}, using latitude and longitude reported for each contributed dataset.}
    \label{fig:figureSI1}
\end{figure}
